DeepPicar: A Low-cost Deep Neural Network-based Autonomous Car

### 2018-04-19 paper/related.tex
..

In this paper, we have analyzed real-time performance of a
state-of-the art CNN, used in NVIDIA's DAVE-2 self-driving car, on a
low-cost raspberry pi 3 quad-core platform. It should be noted,
however, that DAVE-2's CNN we used here is relatively small compared
to recent state-of-the-art CNNs, which are increasingly larger and
deeper. For example, the CNN based object detector models evaluated in
Google's recent study~\cite{huang2017speed} have between 3M to 54M
parameters. Using such large CNN models will be challenging on
resource constrainted embedded computing platforms, especially for
real-time applications such as self-driving cars.

>>>>

In this paper, we have analyzed real-time performance of a CNN, which
was used in NVIDIA's DAVE-2 self-driving car~\cite{Bojarski2016}, on a 
low-cost raspberry pi 3 quad-core platform. It should be noted,
however, that DAVE-2's CNN is relatively small compared
to recent state-of-the-art CNNs, which are increasingly larger and
deeper. For example, the CNN based object detector models evaluated in
Google's recent study~\cite{huang2017speed} have between 3M to 54M
parameters, much larger than DAVE-2's CNN.
Using such large CNN models will be challenging on
resource constrainted embedded computing platforms, especially for
real-time applications such as self-driving cars.
